### 2011-05-13 paper/paper.tex
editted the intro a bit

It is known that all of these transition functions have a uniform stationary distribution, and that the distributions of the Markov chain eventually converge to these uniform distributions. In theory, the hit-and-run method converges much more quickly: the Metropolis methods require in the worst case at least an amount of time exponential in the number of dimensions $n$ to get an approximation to the uniform distribution that is within the desired precision, whereas the hit-and-run method requires only polynomial time regardless of the starting distribution. In this paper we introduce \emph{adaptive Metropolis}, modifications which adjust the transition distribution in hopes of reducing the required time in practice, although we are not aware of any theoretical improvements.

>>>>

It is known that all of these transition functions have a uniform stationary distribution, and that the distributions of the Markov chain eventually converge to these uniform distributions. In theory, the hit-and-run method converges much more quickly: the Metropolis methods require in the worst case at least an amount of time exponential in the number of dimensions $n$ to get an approximation to the uniform distribution that is within the desired precision, whereas the hit-and-run method requires only polynomial time regardless of the starting distribution. In this paper we introduce the \emph{adaptive Metropolis} method, a modification of the basic Metropolis method which adjusts the transition distribution as it runs, trying to balance out a couple of factors which impede its ability to travel throughout the entire region that we will see later. The hope is that it reduces the number of transitions needed in practice, although we are not aware of any theoretical improvements.
